Influence of Connectivity on Dung Beetle Communities

### 2025-05-29 corridor_docs/eric_ms_thesis/MS_thesis.Rmd
super minor tweaks.

Biodiversity between patch types was compared using Hill numbers (Jost 2006). Hill numbers are....  They are an alternative to...We looked at community composition by increasing magnitudes of diversity components (qD) of 0D (species richness), 1D (Shannon entropy), and 2D (Simpson Diversity). Diversity numbers were calculated in R studio using package hillR and modeled using package lme4. For the purposes of this project richness was modeled using a generalized linear mixed model with a poisson distribution. A qqplot of our data shows that our residuals are normally distributed (Figure 1).

>>>>

Biodiversity between patch types was compared using Hill numbers (Jost 2006). Hill numbers are metrics developed with the goal of providing a unifying context for the quantification of the many ways we measure biodiversity. [delete: In our work, we use Hill numbers to explore the impacts of abundance in our diversity measurements]. They are an alternative to more specialized metrics such as _________, which are less intuitive for interpretation. [maybe a sentence on how / why hill numbers are easier to interpret?]  We looked at [compared] community composition by increasing magnitudes of diversity components (qD) of 0D (species richness), 1D (Shannon entropy), and 2D (Simpson Diversity). [can you add a sentence about how these are calculated? by whihc I mean - are the calculations different than for richness, shannon, etc.?] Diversity numbers and species richness were calculated in R studio using package `hill`.

To test for the effects of connectivity on species abundance, richness, and diversity [we compared the values of the Hill Shannon and Simpson indexes in the different patch types and matrix]. For abundance and richness we used generalized linear mixed models (i.e., GLMM) fitted to a poisson distribution. We looked at [compared...looked at sounds squishy. try to use more active verbs like compared, quantified, assessed, etc.] (1) the overall species richness and (2) the abundance of the top 6 most common species in each patch type. We included the identity of the sampling block as a random effects. To model our diversity metrics we took a similar approach, but this time using GLMMs with a Gaussian distribution. All models were fit using `lme4` package.  Prior to conducting our modeling we used _qqplots_ (`DARMa` package) to evaluate the the suitability of our data.
